---
title: "DSCI445 - Term Presentation"
authors: "Jason Nero"
date: "Due 12/05/2022 by 6:10pm"
output: pdf_document
---

```{r, message=FALSE, warning=FALSE}
#libraries
library(dplyr)
library(tidymodels)
library(tidyverse)
library(ggplot2)
library(GGally)
library(caret)
library(leaps)
library(dplyr)
```

```{r}
#setup
data <- read.csv("HockeyData.csv")
df <- data.frame(data)
data.c <- df %>% filter(Year > 2016)
```


```{r}



```


```{r}
# check for NA values.  
sum(is.na(data.c))
```

```{r}
# Initial exploration
## Correlation map 
wo.team <- data.c [,-which(names(data.c) == "Team")]
ggpairs(wo.team)
```

```{r}
#fit basic model 
lm.fit <- lm(TotalFights ~ ., data.c)
summary(lm.fit)
```

It could appear that none of variables are statically significant with the exception of the fights subcatgoires, which makes sense Totalfights is based off them, and surprisingly Montreal Canadians. 

```{r}

plot(data.c$Year, data.c$TotalFights, xlab = "Year", ylab = "Total Fights")

plot(data.c$Attendence, data.c$TotalFights)
plot(data.c$Win, data.c$TotalFights)
plot(data.c$Lose, data.c$TotalFights)
plot(data.c$Lose, data.c$TotalFights)
plot(data.c$Rank, data.c$TotalFights)
plot(data.c$Points, data.c$TotalFights)
plot(data.c$Goalsfor, data.c$TotalFights)
plot(data.c$Goalsagainst, data.c$TotalFights)
plot(data.c$TotalFights, data.c$Teams)
#ggplot this section with year as color (minus first one).  

```

Year/TotalFights: Interesting to see that in 2020 there was no physical attendance due to COVID restrictions fights still occured and in somewhat in line with other years.

```{r}
#filter by team and sum to get total fights overall 
teams.totals <- data.c %>% group_by(Team) %>% summarise(Freq = sum(TotalFights))
teams.totals
ggplot(teams.totals, aes(x=Team, y=Freq)) + geom_col() + scale_x_discrete(guide = guide_axis(angle = 90)) + labs(y = "Totalfights (2017-2021)")
```



```{r}
#split data set randomly 60/40 
cut <- floor(nrow(data.c) * 0.6) 
split <- sample(dim(data.c)[1],cut)
train.h <- data.c[split,]
test.h <- data.c[-split,] 
```


```{r}
#determine significant variables
sub_sel <- regsubsets(TotalFights~., data = data.c, nvmax = 15)

#Mallow's CP - lowest
cp <- summary(sub_sel)$cp
cp
#Bayesian information criterion - lowest
bic <- summary(sub_sel)$bic
bic
#Adjusted R^2 - Highest
adjr2 <- summary(sub_sel)$adjr2
adjr2
#plots
par(mfrow = c(2,2))
plot(cp, type = "l", col = "red")
plot(bic, type = "l", col = "blue")
plot(adjr2, type = "l", col = "green")
```

```{r}
data.train <- data.frame(y = train.y, x = train.x)
reg.train <- regsubsets(y ~ ., data = data.train, nvmax = 20)

d.test <- data.frame(y = test.y, x = test.x)
test.matrix <- model.matrix(y ~ ., data = d.test, nvmax = 20)

t.errors <- rep(NA, 20)

for (i in 1:20) {
    coefi <- coef(reg.train, id = i)
    pred <- test.matrix[, names(coefi)] %*% coefi
    t.errors[i] <- mean((pred - test.y)^2)
}

plot(t.errors, type = "b")
```    



```

```{r}
#determine significant model
#include cv


```
