---
title: "TermProject_Presentationv2"
author: "Sarah Sublett"
date: '2022-12-02'
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Ever Go to a Boxing Match and a Hockey Game Breaks Out? 
Or an Exploration into the Incidence of Fights in Professional Hockey Games.

  Chien Lin

  Jason Nero

  Sarah Sublett

DSCI 445
5 December 2022

## Motivation

- General interest in the impact of fines imposed by the NHL to curb fighting during professional hockey games. 
- Fighting at the professional level encourages similar behavior in junior leagues, and fighting can lead to serious injuries.

## Data

- Utilizing fight data from hockeyfights.com and 
- Refined fight data to years 2017-2021 due to incomplete data 
-  Initial data set included over 2000 entries and was refined to 156 entries 
	- each entry represents the number of fights each team had per year evaluated
- 32 teams in the NHL
- 1,312 games per regular season, with each team playing 82 games

## Application of DSCI 445 Concepts

Utilized:
- ggplot
- lm
- splitting dataset to train and test
- Ridge regressions
- adjusted R-squared
- BIC

## Variables Evaluated


## Challenges with Data

- Readily available or consolidated data, had to combine multiple sources to form dataset
- Several teams were created during the time frame, creating incomplete information
- Utilized omit.na code to compensate
- pre-fight, post-fight, and in-season fighting
- availability of more information on the specifics of the fight (time in the game, type, number of people in the fight, instigator versus respondent of the fight, etc).

## Findings

-It could appear that none of the variables are statically significant, with the exception of the fights subcategories, which makes sense Totalfights is based on them. 

- Surprisingly, Montreal Canadians, during the initial look, appeared to be statistically significant, yet in more robust analysis, it was not. 

-Year/TotalFights: Interesting to see that in 2020 there was no physical attendance due to COVID restrictions; fights still occurred and in somewhat in line with other years.

## Plots of Interest

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
## Future Work

Explore additional variables and develop or acquire a more robust dataset to perhaps look at different violations and the impact of the fines on fighting. 

More time to further evaluate the data.

## References

hockeyfights.com
NHL.com